---
title: "lendingapproved"
author: "GAN LING"
date: "2017/3/28"
output: html_document
---
    
*load data, save the data to RData, accelerate the speed *   

```{r}
# rejectdata = read.csv("RejectStatsA.csv")
load("RejectStatsA.RData")
# lendingdata = read.csv("LC2007-2012.csv")
load("LC2007-2012.RData")
```

*select the variables we want to predict*

```{r}
rej = rejectdata[,c("Amount.Requested","Risk_Score","Debt.To.Income.Ratio","Employment.Length")]
colnames(rej) = c("amount","score","dti","employment")
lend = lendingdata[,c("loan_amnt","mths_since_last_delinq","dti","emp_length")]
colnames(lend) = c("amount","score","dti","employment")
```

*deal with NA data and score == 0 data*

```{r}
rej = na.omit(rej)
rej = subset(rej, score!=0)
lend = na.omit(lend)
lend = subset(lend, score!=0)
```

*transform all of the data into number, not a string*

*first to deal with rej*

```{r}
# see the type of the variables
str(rej)
# then we need to deal with dti and employment
rej = transform(rej, dti=gsub("%","",dti))
rej$dti = as.numeric(rej$dti)
# see the structure of employment
table(rej$employment)
# we notice that there are some n/a rows, omit them
rej = subset(rej, employment!="n/a")
rej$employment = ifelse(rej$employment=="< 1 year",0,gsub("[+]? year[s]?","",rej$employment))
rej$employment = as.numeric(rej$employment)
str(rej)
```

*then deal with lend data*

```{r}
# see the type of the variables
str(lend)
# then we need to deal with employment
# see the structure of employment
table(lend$employment)
# we notice that there are some n/a rows, omit them
lend = subset(lend, employment!="n/a")
lend$employment = ifelse(lend$employment=="< 1 year",0,gsub("[+]? year[s]?","",lend$employment))
lend$employment = as.numeric(lend$employment)
str(lend)
```

*standarize the data*

```{r}
lend = scale(lend)
rej = scale(rej)
```

*define the data, lend is agree data, rej is reject data*

```{r}
lend = data.frame(lend, agree.loan = 1)
rej = data.frame(rej, agree.loan = 0)
lend$agree.loan = as.factor(lend$agree.loan)
rej$agree.loan = as.factor(rej$agree.loan)
wholedata = rbind(lend, rej)
```

*Then we can define the training set and test set*

```{r}
require(caret)
seed = as.numeric(as.Date("2017-03-28"))
set.seed(seed)
inTrain = createDataPartition(wholedata$agree.loan, p=0.7)
trainingset <- wholedata[inTrain[[1]],]
testset = wholedata[-inTrain[[1]],]
```

*Use different approaches to predict the data*

*use GLM to do the predict*

*train the data*

```{r}
glm.fit = glm(agree.loan~.,data = trainingset,family = binomial)
summary(glm.fit)
```

*predict the data using testset and glm.fit*

```{r}
glm.probs = predict(glm.fit, newdata = testset, type = "response") 
glm.probs[1:5]
glm.pred = ifelse(glm.probs > 0.5, 1, 0) 
confusionMatrix(glm.pred, testset$agree.loan)
```

*use knn to do the predict*

*train the data*

```{r}
library(class)
knn.pred = knn(trainingset,testset,trainingset$agree.loan, k = 1)
confusionMatrix(knn.pred, testset$agree.loan)
```